manuscript

### 2022-09-12 ms/manuscript.Rmd
make template

---
title: "manuscript"
author: "Daniel Suh"
date: "2022-09-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "manuscript"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
---

# Introduction

# Methods

# Results

# Discussion

# References
